### 2019-04-08 3_task_bench.tex
Fiddle with spacing and text to make things fit again.
apply some of Yuankun's comments

Task Bench provides two main kernels that can be called from tasks,
which are compute- and memory-bound, respectively. The compute-bound
kernel executes a tight loop and is hand-written using AVX2 FMA
intrinsics. The memory-bound kernel performs sequential reads and
writes over an array, and is again hand-optimized with AVX2
intrinsics. The duration of both kernels can be configured by setting
the number of iterations to execute; we use this ability to simulate
the effects of varying application problem sizes. The memory-bound
kernel is carefully written to keep the working set size constant as
the number of iterations decrease, to avoid unwanted speedups due to
cache effects.

>>>>

Task Bench provides two main kernels that can be called from tasks,
which are compute- and memory-bound, respectively. The compute-bound
kernel executes a tight loop and is hand-written using AVX2 FMA
intrinsics. The memory-bound kernel performs sequential reads and
writes over an array, and is again hand-optimized with AVX2
intrinsics. The duration of both kernels can be configured by setting
the number of iterations to execute; we use this ability to simulate
the effects of varying application problem sizes. The memory-bound
kernel is carefully written to keep the working set size constant as
the number of iterations decreases, to avoid unwanted speedups due to
cache effects.
